---
title: "Run SWATplus with given parametersets"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Run SWATplus with given parametersets}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

### 1. Overview
This vignette describes how to perform forward runs (without calibration) of SWAT+ with given parameter sets. This could be used, for example, (1) to run the model with behavioral parameter sets for a specific scenario, (2) to re-run the model with the best parameter set to examine all other model outputs that were not extracted during model calibration, etc.


### 2. Require data
For such a forward run, we need the following data:

* TxtInOut of SWAT+ 
* A text file contains parameters set that we want to run
* cal_parms.cal file

### 3. Input configuration
In the following R Script, the lines start with "TODO" need to be change by users

```{r, message=FALSE, eval = FALSE}
library(RSWAT)

# 1.Create an example TxtInOut of SWAT+ (TODO: remove this command if you already # had the TxtInOut folder of SWAT+)
extracExampleData(exampleData, "swatPlusTxtInOut", tempdir())

# 2.Path to the TxtInOut folder (TODO: replace with your TxtInOut path)
TxtInOutFolder <- file.path(tempdir(), "swatPlusTxtInOut")

# 3.This is a SWAT+ project, therefore
SWATproject <- FALSE

# 4.My working directory (TODO: change to your desired working directory)
# dir.create(file.path(tempdir(), "workingFolder"))
workingFolder <- file.path(tempdir(), "workingFolder")

# 5.Path of the SWAT executable file (TODO: replace with your path)
SWATexeFile <- "C:/data/rev60.5.7_64rel.exe"

# 6.Path of the SWAT+ parameter file cal_parms.cal (TODO: replace with your path)
SWATParamFile <- file.path(TxtInOutFolder, "cal_parms.cal")

# 7.The parameters that I previously used for model calibration (TODO: change to your paraSelection)
paraSelection <- data.frame(
   Parameter = c("cn2.hru"   , "canmx.hru"),
   Change =    c("relative"  , "replace"),
   Min =       c(-0.25       , 1.0),
   Max =       c(0.25        , 10.0),
   Object  =   c("All"       , "All"),
   Conditions = c("All"      , "All")
   )

# You can also create these above table by the interface of R-SWAT then save 
# the  project. If you do so, you can extract that table from the RSWATproject.rds 
# file in the working folder (TODO: Delete if you don't read from RSWATproject.rds)

# RSWATproject <- readRDS("C:/data/RSWATproject.rds")
# paraSelection <- RSWATproject$paraSelection
  
# 8. How parameters should be generated
samplingApproach <- "Read_User_Parameter_File"  # Do not change this line

# 9. Output extraction for SWAT+ can be created manually or by the GUI (TODO: change this)
outputExtraction <- data.frame(
   FileType = c("channel_sd_day.txt"),
   FileName = c("channel_sd_day.txt"),
   Column = c("48"),
   Reach = c("1") # E.g., for 100 reaches use: Reach = paste(as.character(c(1:100)), collapse  = ",")
 )

# 10. Date range for extraction (TODO: change this)
dateRangeCali <- as.Date(c("2003-01-01", "2012-12-31"), format = "%Y-%m-%d")

# 11. Number of parallel runs  (TODO: change  this)
ncores <- 2

# 12.  Generate parameter samples using Latin Hypercube Sampling (TODO: change this)
parameterValue <- as.matrix(read.table(file = "C:/data/user_parameter_values.txt",
                                       header = TRUE, sep =""))

# Here is the content of my user_parameter_values.txt"
#cn2.hru         canmax.hru
#0.10            1.5
#-0.20           3.0
#-0.10           0.2
#0.22            1.0
#

# Remove the column names and number these parametersets from 1 to n. DONOT change this
parameterValue <- cbind(c(1:nrow(parameterValue)),parameterValue)
colnames(parameterValue) <- NULL
rownames(parameterValue) <- NULL

```


### 4. Run SWAT+

Now run SWAT+ with the above settings

```{r, message=FALSE, eval = FALSE}
# Get HRU infor (HRU names, landuse, soil, slope, subbasin)
HRUinfo <- read.table(file.path(TxtInOutFolder, "hru-data.hru"), 
                      header = TRUE, skip = 1, sep = "")

# Read SWAT parameter
SWATParam <- loadSwatParam(SWATParamFile)

# Get location of parameters in TxtInOut files and load TxtInOut file content
caliParam <- updatedFileContent(HRUinfo,paraSelection,SWATParam,
                                TxtInOutFolder)

# Set first run is true so R-SWAT will delete previous simulation
firstRun <- TRUE
copyUnchangeFiles <- TRUE

# Get content of the file.cio file (about simulation time)
fileCioInfo <- getSimTime(TxtInOutFolder)

# Now start to run SWAT
runSWATpar(workingFolder,TxtInOutFolder,outputExtraction,ncores,SWATexeFile,
           parameterValue,paraSelection,caliParam,copyUnchangeFiles,fileCioInfo,
           dateRangeCali,firstRun)

```


### 4. Processing model output

```{r, message=FALSE, eval = FALSE}

# Read all output_var_xx.txt files in the workingFolder/Output/Core_xx
# First you need to you how many output time steps for each variables 
# You can open the out_var_xx.txt and check, below lets assume I only have one 
# output variable, for more detail see function readAllOutVar
# TODO: change numTimesteps. Example, for 100 output variables with the same time 
#                            steps of 24 please use: numTimesteps <- rep(24,100)

numTimesteps <- c(3653) 
output <- readAllOutVar(workingFolder, numTimesteps)

# Now calculate the 95PPU (SUFI2 approach) for each output variables, example for variable 1
# TODO: change variable and percentiles as your wish
variable <- 1
percentiles <- c(0.025, 0.5, 0.975)

for (itime in 1:nrow(output[[variable]])){
  ppu <- as.numeric(quantile(output[[variable]][itime,],percentiles))
  if (itime == 1){
    ppu95 <- ppu
  } else {
    ppu95 <- rbind(ppu95, ppu)
  }
}

# Give it a column names
colnames(ppu95) <- c("lower95PPU", "median95PPU", "upper95PPU")
row.names(ppu95) <- NULL

```


### References




