---
title: "Use user-defined output extraction"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Use user-defined output extraction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

### 1. Overview
As SWAT/SWAT+ have many outputs, RSWAT only provides some standard output extraction. Users want to extract other model outputs can implement their own output extraction function and replace the userReadSwatOutput function in RSWAT

### 2. Import your design objective function into RSWAT
Depending on whether you use RSWAT with our without the GUI

* Case 1: When you used the GUI of RSWAT, the user objective function can be imported in step 3. Run SWAT  &rarr. 1. Define model outputs for extraction

* Case 2: When using RSWAT without the GUI, user needs to add the following line to their script:
 
```{r, message=FALSE, eval = FALSE}
# TODO change file path to your userObjFunction.R file
source("C:/example/userReadSwatOutput.R")
```

### 3. How to create userObjFunction.R file?

Below is a minimum example of a user defined output extraction. Lets say we run SWAT model and want to extract data in the 7th column of the file  output.rch and aggregate to monthly.

Here is the content of the "userReadSwatOutput.R" file for such a task

```{r, message=FALSE, eval = FALSE}

#' User-defined function for reading SWAT/SWAT+
#'
#' @description
#' This is a user-defined function for reading SWAT/SWAt+ outputs, do not use
#' as it is now, please modify the source code of this function if you use
#' according to your need and then install RSWAT app again from your local
#' folder to update this function.DO NOT CHANGE the name of this function
#' (mus be updateUserReadSwatOutput). ONLY CHANGE the code at the place where indicates
#' "START TO CHANGE FROM HERE" and STOP at "END OF CHANGE". This functions
#' must NOT receive any input. By default, you are NOW INSIDE the TxtInOut folder
#' and you can read any output files there by just using the file name.
#' RSWAT will use this function to get SWAT outputs (from the respective core)
#' after each model run and save it in combination with other outputs.
#'
#' Please TEST your function before running R-SWAT
#'
#' @return a list of vector (of simulated data)
#' @importFrom stats aggregate
#'
#'
#' @export
#'

updateUserReadSwatOutput <- function(){
  
  output <- list()
  # -------------------------------------------------------------------------#
  #       Delete the existing code below and add your code below this line   #
  #                 START TO CHANGE FROM HERE                                #
  # -------------------------------------------------------------------------#
  # Example: This function extracts data in the 7th column of the file  output.rch
  #          and aggregate to monthly
  
  # --------------------------------------------------------------------------
  date <- seq(from = as.Date("2010-01-01", "%Y-%m-%d"),
              to = as.Date("2020-12-31", "%Y-%m-%d"),
              by = 1)
  year <- as.numeric(format(date, "%Y"))
  month <- as.numeric(format(date, "%m"))
  
  # Reach number to extract
  reachNumber <- c(17, 42, 48, 61)
  
  # --------------------------------------------------------------------------
  
  # Read all data from output.rch
  getOutputRsvData <- read.table("output.rch", header = FALSE, sep = "", skip = 9)
  
  # Only select column 7 (this is the outflow column)
  flowOut <- getOutputRsvData[,7]
  
  # Total number of reach
  totalNumberOfReach <- max(getOutputRsvData[,2])
  
  # Get daily outflow of each reach and aggregate to monthly flow (unit m3/month)
  for (i in 1:length(reachNumber)){
    
    # Get daily outflow of reach reachNumber[i]
    output[[i]] <- flowOut[seq(reachNumber[i], length(flowOut), totalNumberOfReach)]
    
    # Put daily outflow to a data frame of 3 columns (month, year, and daily Q)
    dataFrame <- data.frame(month = month,
                            year = year,
                            Q = output[[i]])
    
    # Aggregate to monthly
    dataFrameMonthly <- aggregate(.~ month + year, dataFrame, FUN = sum)
    
    # Only get the values of Q
    output[[i]] <- dataFrameMonthly$Q
    
  }
  
  # ----------------------------------------------------------------------------
  # END OF CHANGE: Don't modify anything after this line
  # ----------------------------------------------------------------------------
  
  return(output)
  
}

# Overwrite the userReadSwatOutput with our updateUserReadSwatOutput
environment(updateUserReadSwatOutput) <- asNamespace('RSWAT')
assignInNamespace("userReadSwatOutput", updateUserReadSwatOutput, ns = "RSWAT")

```




