---
title: "Use user-defined objective function"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Use user-defined objective function}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

### 1. Overview
When the build-in objective functions of RSWAT (e.g., NSE, KGE, PBIAS, ...) do not suit your need, here is the place you can define a custom objective function.

### 2. Import your design objective function into RSWAT
Depending on whether you use RSWAT with our without the GUI

* Case 1: When you used the GUI of RSWAT, the user objective function can be imported in step 4.1. Objective function &rarr; 1. Select objective function (userObjFunction) &rarr; Load userObjFunction.R

* Case 2: When using RSWAT without the GUI, user needs to add the following line to their script:
 
```{r, message=FALSE, eval = FALSE}
# TODO change file path to your userObjFunction.R file
source("C:/example/userObjFunction.R")
```

### 3. How to create userObjFunction.R file?

Below is a minimum example of a user defined objective function. Lets say we simulate for streamflow (Q) in two gauging stations (station 1 and station 2). In the first gauging stations, we use the Root Mean Square Error (RMSE) as an objective function but put more weight on streamflow of the second gauging station. Our final RMSE should has the following form:

$$ R^2 = \frac{1 \cdot R^2_{Q_1} + 2 \cdot R^2_{Q_2}}{1 + 2} $$
Here is the content of the "userObjFunction.R" file

```{r, message=FALSE, eval = FALSE}
#' User-defined objective function - DO NOT USE AS IT IS NOW
#'
#' @description
#' This is a user-defined objective function, do not use as it is now, please
#' modify the source code of this function if you use according to your need.
#' DO NOT CHANGE the name of this function (mus be userObjFunction). ONLY CHANGE
#' the code at the place where indicate "START TO CHANGE FROM HERE" and STOP
#' at "END OF CHANGE".
#'
#' @param obs a list of observed data, for example, time series of the first
#' observed variable is obs[[1]], of the second observed variable is obs[[2]],
#' and so on...
#' @param sim a list of simulated data, sim[[1]] corresponds to obs[[1]], and so
#' on...
#'
#' @return a data frame contains a single objective function value
#' @importFrom stats cor
#' @examples
#'
#'\donttest{
#' userObjFunction(obs, sim)
#'}
#'
#' @export
#'

userObjFunction <- function(obs, sim){

  # obs is a list of observed variables
  # obs[[1]] is a vector of the first observed variable
  # obs[[2]] is a vector of the second observed variable, and so on...
  # obs[[...]]

  # sim is a list of simulated variables
  # sim[[1]] is a vector of the first simulated variable
  # sim[[2]] is a vector of the second simulated variable, and so on...
  # sim[[...]]

  # The actual number of variables is defined in step 4. Run SWAT -> 1. Output extraction

  # Remove missing values from the observed and the corresponding values in simulated data

  for (i in 1:length(obs)){

    # Find index of missing values in observed data
    missingValue <- which(is.na(obs[[i]]))

    # Remove missing values
    if (length(missingValue) > 0){
      obs[[i]] <- obs[[i]][-missingValue]
      sim[[i]] <- sim[[i]][-missingValue]
    }
  }

  # Define output variable
  output <- list()
  output$perCriteria <- list()

  # -------------------------------------------------------------------------#
  #  TODO: MODIFY the existing code below and add your code below this line  #
  #                 START TO CHANGE FROM HERE                                #
  # -------------------------------------------------------------------------#
  # In this example, lets say you extracted two outputs and want to calculate
  #                  R square and put more weight to the second variable
  #
  #  output <- (1 * R2_Q_1 + 2 * R2_Q_2)/(1 + 2)
  
  # MUST USE output$perCriteria[[x]] where x indicate the the objective 
  #                                 function values for variable x^th
  
  # MUST USE output$overalPerCriteria for the overall objective function value

  # R2 of the first variable
  output$perCriteria[[1]] <- cor(obs[[1]], sim[[1]])**2

  # R2 of the second variable
  output$perCriteria[[2]] <- cor(obs[[2]], sim[[2]])**2

  # Final objective function value
  output$overalPerCriteria <- (1*output$perCriteria[[1]] + 2*output$perCriteria[[2]])/3

  # ----------------------------------------------------------------------------
  # END OF CHANGE: Don't modify anything after this line
  # ----------------------------------------------------------------------------
  for (i in 1:length(output$perCriteria)){
    output$perCriteria[[i]] <- data.frame(userObjFunc = output$perCriteria[[i]])
  }

  return(output)
}


# Overwrite the userObjFunction with our updatedUserObjFunction
environment(updatedUserObjFunction) <- asNamespace('RSWAT')
assignInNamespace("userObjFunction", updatedUserObjFunction, ns = "RSWAT")

```




